hbm_paper_results

### 2023-12-27 paper_results.Rmd
qc for centiles at 0 and 1

# tidy(lm(mean_centile ~ mean_cent_diff, data= ratio_subj_list[[1]]))
# summary(lm(mean_centile ~ mean_cent_diff, data= ratio_subj_list[[1]]))
```
# Main Analyses

@@

unique(qc_z_df$participant)
ppt.list
```

@@

>>>>

# tidy(lm(mean_centile ~ mean_cent_diff, data= ratio_subj_list[[1]]))
# summary(lm(mean_centile ~ mean_cent_diff, data= ratio_subj_list[[1]]))
```

# Main Analyses

@@

unique(qc_z_df$participant)

qc_cent_df %>%
  dplyr::filter(centile != 1) %>%
  summarize(sprintf("%.100f", (1 - max(centile))))

qc_cent_df %>%
  summarize(sprintf("%.100f", min(centile)))
```

@@

##CENTILE FANS

pulled predicted centiles from cubic using `scp -r 'gardnerm@cubic-login.uphs.upenn.edu:/cbica/home/gardnerm/combat-biovar/ukb_basic/centile_csvs/*_centiles.csv' .`

```{r}
basic_data_path <- "/Users/megardn/Desktop/BGD_Repos/combat_biovar/derivatives/ukb_basic"
raw_files <- list.files(path = basic_data_path, pattern = "_centiles.csv", full.names = TRUE)

    data <- data %>%
     mutate(dataset = gsub("-data", "", dataset))

    # Bind the data to the combined dataframe
    df_list[[file]] <- as.data.frame(data)
    assign("basic_centiles", df_list)
}
length(basic_centiles)
centiles.df <- bind_rows(basic_centiles)
skimr::skim(centiles.df)
```

```{r}
#also load raw data
ukb_cn_df <- fread("/Users/megardn/Desktop/BGD_Repos/combat_biovar/data/ukb_to_model/ukb_CN_data_simsites.csv")
```

just work with global volumes for now

```{r}
global.cent.df <- centiles.df %>%
  dplyr::filter(pheno_cat == "Global Volume")

global.cent.df %>%
  group_by(pheno) %>%
  summarise(max=max(centile_5))

names(global.cent.df)

gmv.df <- global.cent.df

gmv.df <- centiles.df %>%
  dplyr::filter(pheno =="GMV")

  ggplot(gmv.df) +
      #geom_point(aes(x=ukb_cn_df$age_days, y=ukb_cn_df$GMV), alpha=0.5) +
      #scale_colour_manual(values=c("#5AAE61FF", "#9970ABFF")) +
      geom_line(aes(x=gmv.df$age_days, y=gmv.df$M_centile_1, color=gmv.df$dataset)) +
      geom_line(aes(x=gmv.df$age_days, y=gmv.df$M_centile_2, color=gmv.df$dataset)) +
      geom_line(aes(x=gmv.df$age_days, y=gmv.df$M_centile_3, color=gmv.df$dataset)) +
      geom_line(aes(x=gmv.df$age_days, y=gmv.df$M_centile_4, color=gmv.df$dataset)) +
      geom_line(aes(x=gmv.df$age_days, y=gmv.df$M_centile_5, color=gmv.df$dataset)) +
      facet_wrap(~ pheno, scales="free_y") + 
      labs(title="Male GMV brain charts")

      geom_line(aes(x=ages, y=pred$fanCentiles[[2]])) +
      geom_line(aes(x=ages, y=pred$fanCentiles[[3]]), alpha=0.6) +
      geom_line(aes(x=ages, y=pred$fanCentiles[[4]]), alpha=0.8) +
      geom_line(aes(x=ages, y=pred$fanCentiles[[5]])) +
      geom_line(aes(x=ages, y=pred$fanCentiles[[6]]), alpha=0.8) +
      geom_line(aes(x=ages, y=pred$fanCentiles[[7]]), alpha=0.6) +
      geom_line(aes(x=ages, y=pred$fanCentiles[[8]]), alpha=0.4) +
      geom_line(aes(x=ages, y=pred$fanCentiles[[9]]), alpha=0.2) +
      geom_point(aes(x=peak_age, y=pred$peak), size=3) +
      scale_x_continuous(breaks=tickMarks, labels=tickLabels,
                         limits=c(tickMarks[[1]], max(age_col))) +
      labs(title=deparse(substitute(gamlssModel))) +
      theme(legend.title= element_blank())+
      xlab(paste("Age at Scan", unit_text)) +
      ylab(deparse(substitute(phenotype)))
    annotate("text", x = max(age_col)-0.5, y = max(yvar)-10000, label = paste0("BIC=",gamlssModel$sbc))
    print(sampleCentileFan)
```
